Fuels, fire weather, and Rx fire behavior in North Dakota

### 2021-08-06 paper/analysis.Rmd
finish first draft

---
title: Fuels, fire weather, and Rx fire behavior in North Dakota
subtitle: Finalizing figures and results
date: '`r Sys.Date()`'
author: DAM
output:
  html_document:
    keep_md: false
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, echo=FALSE, warning=FALSE, message = FALSE, results='hide'}
knitr::opts_chunk$set(message = FALSE, warning=FALSE, 
               echo=FALSE, eval=TRUE, fig.path='figures/', dev=c('png', 'pdf')) 
```

```{r data_loading}
# Packages 
  pacman::p_load(tidyverse, readr, mice, broom.mixed, vegan,
                 lubridate, gridExtra, wesanderson)
set.seed(42)
# Data
  fp = url('https://raw.githubusercontent.com/devanmcg/SpatialFireBehavior/main/data/AnalysisDataKY.csv') 
  AnalysisData <- read_csv(fp) 
# Extra scripts
  source("https://raw.githubusercontent.com/devanmcg/IntroRangeR/master/11_IntroMultivariate/ordinationsGGplot.R")
  source('https://raw.githubusercontent.com/cran/mice/master/R/mipo.R')
```

@@

We used the multiple imputation method in the **mice** package to fill in missing values. 
The method creates 5 datasets, each with different but reasonable values for the missing data based on patterns in existing data, and performs the regression analysis on each. 
These results are pooled into a single set of results.

```{r imp, eval=TRUE}
# Calculate imputed datasets on scaled data
  imp_sc <- AnalysisData %>% 
          select(-LAI, -JD) %>%
          mutate_at(vars(AirTemp:tHa), ~as.numeric(scale(., center=F))) %>%
                    mutate(across(location:array, as.factor)) %>%
                     mice(m=5, seed = 23109, print=F)
# Reduce mids object to tibble for multivariate analysis    
    imp_raw <- 
      complete(imp_sc, 'long') %>%
      as_tibble() %>%
      unite("TreeID", c(location, block, pasture,
                        year, plot, array), sep = ".") %>%
      select(-patch, -.id, -.imp, -FireCode) %>%
      pivot_longer(names_to = "response", 
                   values_to = "values", 
                   -TreeID) %>%
      group_by(TreeID, response) %>%
      summarize(value = median(values)) %>%
      ungroup() %>%
      pivot_wider(names_from = response, 
                  values_from = value) %>%
      separate(TreeID, c("location", "block", "pasture",
                         "year", "plot", "array")) %>% 
      mutate(across(location:array, as.factor))
```

@@

```{r glmer_mods, eval=TRUE}
# Mixed-effect regression models 
#
# Rate of spread
#   
  # Fit model 
    ros_imp <- with(imp_sc, suppressMessages(
                lme4::glmer(ros ~ RH + WindSpeed + 
                              FuelMoisture + tHa + 
                              (1|location/block/year/plot), 
                            family=Gamma(link = "log"), 
                            control=lme4::glmerControl(optimizer="bobyqa", 
                                                       optCtrl=list(maxfun=100000)) )) )
    ros_imp_pooled <- pool(ros_imp)$pooled  %>%
                          as_tibble()
    # Get terms
    ros_terms <- 
      full_join(
      summary(pool(ros_imp)) %>% 
        as_tibble() %>%
        rownames_to_column("row"),

@@

#
# Maximum canopy temperature  
#
# Fit model 
canopy_imp <- with(imp_sc, suppressMessages(
              lme4::glmer(MaxC ~ RH + WindSpeed +  
                            FuelMoisture + tHa + 
                            (1|location/block/year/plot), 
                          family=Gamma(link = "log"), 
                          control=lme4::glmerControl(optimizer="bobyqa", 
                                                     optCtrl=list(maxfun=100000)) )) )

@@

#
# Maximum soil surface temperature  
#
# Fit model 
  soil_imp <- with(imp_sc, suppressMessages(
                  lme4::glmer(log(SoilMaxC+1) ~ RH + WindSpeed +  
                      FuelMoisture + tHa + 
                      (1|location/block/year/plot), 
                    family=Gamma(link = "log"), 
                    control=lme4::glmerControl(optimizer="bobyqa", 
                                               optCtrl=list(maxfun=100000)) )) )

@@

response_CIs <-   
  bind_rows(
    mutate(soil_terms, response = 'Temp. at surface'), 
    mutate(canopy_terms, response = 'Temp. above surface'),
    mutate(ros_terms, response = "Rate of spread") 
  ) %>%
  as_tibble() %>%
  rename(lwr = `2.5 %`, upr = `97.5 %`) %>%
  filter(term != '(Intercept)') %>%
  mutate(term = recode(term, tHa = 'Fuel load', 
                             WindSpeed = 'Wind speed', 
                             RH = 'Relative humidity', 
                             FuelMoisture = 'Fuel moisture')) 
```

@@

  pca_scores <- lst(species=pca_spp, 
                    vectors=pca_vd)
  pca_scores$spiders <-
    pca_gg$df_spiders %>% 
    rename(PC1 = x, PC2 = y) %>%
    as_tibble()
```

>>>>

---
title: Fuels, fire weather, and Rx fire behavior in North Dakota
subtitle: Finalizing figures and results
date: '`r Sys.Date()`'
author: DAM
output:
  html_document:
    keep_md: false
    toc: false
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, echo=FALSE, warning=FALSE, message = FALSE, results='hide'}
knitr::opts_chunk$set(message = FALSE, warning=FALSE, 
                      echo=FALSE, eval=TRUE) 
```

```{r data_loading}
# Packages 
  pacman::p_load(tidyverse, readr, mice, broom.mixed, vegan,
                 lubridate, gridExtra, wesanderson)
set.seed(42)
# Data
  fp = url('https://raw.githubusercontent.com/devanmcg/SpatialFireBehavior/main/data/AnalysisDataKY.csv') 
  AnalysisData <- read_csv(fp)

  wd = 'C:/Users/devan.mcgranahan/GithubProjects/SpatialFireBehavior/'
# Extra scripts
  source("https://raw.githubusercontent.com/devanmcg/IntroRangeR/master/11_IntroMultivariate/ordinationsGGplot.R")
  source('https://raw.githubusercontent.com/cran/mice/master/R/mipo.R')
```

@@

We used the multiple imputation method in the **mice** package to fill in missing values. 
The method creates multiple datasets, each with different but reasonable values for the missing data based on patterns in existing data, and performs the regression analysis on each. 
These results are pooled into a single set of results.

```{r imp, eval=TRUE}
# Calculate imputed datasets on scaled data
  imp_sc <- AnalysisData %>% 
          select(-LAI, -JD) %>%
          mutate_at(vars(AirTemp:tHa), ~as.numeric(scale(., center=F))) %>%
                    mutate(across(location:array, as.factor)) %>%
                     mice(m=100, seed = 23109, print=F)
# Reduce mids object to tibble for multivariate analysis    
    imp_raw <- 
      complete(imp_sc, 'long') %>%
      as_tibble() %>%
      unite("TreeID", c(location, block, pasture,
                        year, plot, array), sep = ".") %>%
      select(-patch, -.id, -.imp, -FireCode) %>%
      pivot_longer(names_to = "response", 
                   values_to = "values", 
                   -TreeID) %>%
      group_by(TreeID, response) %>%
      summarize(value = median(values)) %>%
      ungroup() %>%
      pivot_wider(names_from = response, 
                  values_from = value) %>%
      separate(TreeID, c("location", "block", "pasture",
                         "year", "plot", "array")) %>% 
      mutate(across(location:array, as.factor))
```

@@

```{r glmer_mods, eval=TRUE}
# Mixed-effect regression models 
#
# Rate of spread
#   
  # Fit model 
    ros_imp <- with(imp_sc, suppressMessages(
                lme4::glmer(ros ~ VPD + tHa + RH +
                              FuelMoisture + WindSpeed + 
                              (1|location/block/year/plot), 
                            family=Gamma(link = "log"), 
                            control=lme4::glmerControl(optimizer="bobyqa", 
                                                       optCtrl=list(maxfun=500000)) )) )
    ros_imp_pooled <- pool(ros_imp)$pooled  %>%
                          as_tibble()
    # Get terms
    ros_terms <- 
      full_join(
      summary(pool(ros_imp)) %>% 
        as_tibble() %>%
        rownames_to_column("row"),

@@

#
# Maximum canopy temperature  
#
# Fit model 
canopy_imp <- with(imp_sc, suppressMessages(
              lme4::glmer(MaxC ~ VPD + tHa +  RH +
                              FuelMoisture + WindSpeed +
                            (1|location/block/year/plot), 
                          family=Gamma(link = "log"), 
                          control=lme4::glmerControl(optimizer="bobyqa", 
                                                     optCtrl=list(maxfun=100000)) )) )

@@

#
# Maximum soil surface temperature  
#
# Fit model 
  soil_imp <- with(imp_sc, suppressMessages(
                  lme4::glmer(log(SoilMaxC+1) ~ VPD + tHa +  RH +
                              FuelMoisture + WindSpeed +
                      (1|location/block/year/plot), 
                    family=Gamma(link = "log"), 
                    control=lme4::glmerControl(optimizer="bobyqa", 
                                               optCtrl=list(maxfun=100000)) )) )

@@

response_CIs <-   
  bind_rows(
    mutate(soil_terms, response = 'Temp. at surface'), 
    mutate(canopy_terms, response = 'Temp. above surface'),
    mutate(ros_terms, response = "Rate of spread") 
  ) %>%
  as_tibble() %>%
  rename(lwr = `2.5 %`, upr = `97.5 %`) %>%
  filter(term != '(Intercept)') %>%
  mutate(term = recode(term, tHa = 'Fuel load', 
                             WindSpeed = 'Wind speed', 
                             RH = 'Relative humidity', 
                             FuelMoisture = 'Fuel moisture', 
                             VPD = 'Vapor Pressure Deficit')) 
save(response_CIs, file = paste0(wd, 'r objects/response_CIs.Rdata'))
```

@@

  pca_scores <- lst(species=pca_spp, 
                    vectors=pca_vd)
  pca_scores$spiders <-
    pca_gg$df_spiders %>% 
    rename(PC1 = x, PC2 = y) %>%
    as_tibble()
  save(pca_scores, file = paste0(wd, 'r objects/pca_scores.Rdata'))
```

### 2021-08-06 paper/analysis2.Rmd
finish first draft

```{r imp, eval=TRUE}
# Calculate imputed datasets on scaled data
  imp_sc <- AnalysisData %>% 
          select(-LAI, -JD) %>%
          mutate_at(vars(AirTemp:tHa), ~as.numeric(scale(., center=F))) %>%
                    mutate(across(location:array, as.factor)) %>%
                     mice(m=100, seed = 23109, print=F)
# Reduce mids object to tibble for multivariate analysis    
    imp_raw <- 
      complete(imp_sc, 'long') %>%
      as_tibble() %>%
      unite("TreeID", c(location, block, pasture,
                        year, plot, array), sep = ".") %>%
      select(-patch, -.id, -.imp, -FireCode) %>%
      pivot_longer(names_to = "response", 
                   values_to = "values", 
                   -TreeID) %>%
      group_by(TreeID, response) %>%
      summarize(value = median(values)) %>%
      ungroup() %>%
      pivot_wider(names_from = response, 
                  values_from = value) %>%
      separate(TreeID, c("location", "block", "pasture",
                         "year", "plot", "array")) %>% 
      mutate(across(location:array, as.factor))
```

### Model specification

Mixed-effect regression models fit with `lme4::glmer` and constructed as follows:

$$y \approx RH + WS + FM + FL + (1|location/year/plot),~ 
\text{family = gamma, link = log}$$

where

$RH$ = Relative humidity,

$WS$ = Average wind speed,

$FM$ = Fuel moisture (from clipped samples),

$FL$ = Fuel load (t/ha from clipped samples)

Weather variables $RH$ and $WS$ were taken from NDAWN stations for the hour in which the fire behavior observation occurred.

All variables were scaled to a common range prior to analysis, and units for each predictor variable are not reported.

Response variables included

* Maximum temperature (C) 15 cm above soil surface (mean of three thermocouples)
* Maximum temperature (C) at soil surface (single thermocouple)
* Rate of spread (m/s) through three points of a 1 m equilateral triangle

Thermocouple data recorded with the open-source [FeatherFlame](https://diyfirescience.info/portfolio/work2/) system.

### Multivariate analysis

Principal Components Analysis (PCA) on fire behavior responses fit with `vegan::rda`. 
Post-hoc group (location) and gradient (fire weather) analysis with `vegan::envfit`.

An additional composite variable, vapor pressure deficit (VPD), was calculated as

$\text{VPD} = e - e_s$

where

$e = 6.11 \cdot 10^{\frac{7.5 \cdot \text{Dewpoint}}{237.3 + \text{Dewpoint}}}$

and

$e_s = 6.11 \cdot 10^{\frac{7.5 \cdot \text{Air temperature}}{237.3 + \text{Air temperature}}}$

@@

```{r data_summary_gg, fig.height=10, fig.width=6}
LongData <- 
  AnalysisData %>%
    select(-LAI, -JD, -MaxWindSpeed) %>%
    pivot_longer(cols = AirTemp:tHa, 
                 names_to = 'var', 
                 values_to = 'value') %>%
    mutate(type = case_when(
                    var %in% c('MaxC', 
                               'SoilMaxC', 
                               'ros') ~ 'Fire behavior', 
                    var %in% c('tHa',
                               'FuelMoisture') ~ 'Fuel', 
                    TRUE ~ 'Weather' ), 
           var = recode(var, 
                        AirTemp = 'Air temperature (°C)', 
                        RH = 'Relative humidity (%)', 
                        dpC = 'Dew point (°C)', 
                        FuelMoisture = 'Fuel moisture (%)', 
                        tHa = 'Fuel load (t/ha)',
                        MaxC = 'Flame temp (°C)', 
                        WindSpeed = 'Wind speed (m/s)', 
                        ros = 'Rate of spread (m/s)', 
                        SoilMaxC = 'Soil surface temp (°C)'), 
           location = recode(location, 
                             H = "Hettinger", 
                             CG = "Central Grasslands"))

@@

```{r glmer_mods, eval=TRUE}
# Mixed-effect regression models 
#
# Rate of spread
#   
  # Fit model 
    ros_imp <- with(imp_sc, suppressMessages(
                lme4::glmer(ros ~ VPD + tHa + RH +
                              FuelMoisture + WindSpeed + 
                              (1|location/block/year/plot), 
                            family=Gamma(link = "log"), 
                            control=lme4::glmerControl(optimizer="bobyqa", 
                                                       optCtrl=list(maxfun=500000)) )) )
    ros_imp_pooled <- pool(ros_imp)$pooled  %>%
                          as_tibble()
    # Get terms
    ros_terms <- 
      full_join(
      summary(pool(ros_imp)) %>% 
        as_tibble() %>%
        rownames_to_column("row"),

      confint.mipo(pool(ros_imp)) %>%
        as_tibble() %>%
        rownames_to_column("row") )

#
# Maximum canopy temperature  
#
# Fit model 
canopy_imp <- with(imp_sc, suppressMessages(
              lme4::glmer(MaxC ~ VPD + tHa +  RH +
                              FuelMoisture + WindSpeed +
                            (1|location/block/year/plot), 
                          family=Gamma(link = "log"), 
                          control=lme4::glmerControl(optimizer="bobyqa", 
                                                     optCtrl=list(maxfun=100000)) )) )

  canopy_imp_pooled <- pool(canopy_imp)$pooled  %>%
                      as_tibble()

  canopy_terms <- 
    full_join(
      summary(pool(canopy_imp)) %>% 
        as_tibble() %>%
        rownames_to_column("row"),

      confint.mipo(pool(canopy_imp)) %>%
        as_tibble() %>%
        rownames_to_column("row") )

#
# Maximum soil surface temperature  
#
# Fit model 
  soil_imp <- with(imp_sc, suppressMessages(
                  lme4::glmer(log(SoilMaxC+1) ~ VPD + tHa +  RH +
                              FuelMoisture + WindSpeed +
                      (1|location/block/year/plot), 
                    family=Gamma(link = "log"), 
                    control=lme4::glmerControl(optimizer="bobyqa", 
                                               optCtrl=list(maxfun=100000)) )) )

soil_imp_pooled <- pool(soil_imp)$pooled  %>%
  as_tibble()

soil_terms <- 
  full_join(
    summary(pool(soil_imp)) %>% 
      as_tibble() %>%
      rownames_to_column("row"),

    confint.mipo(pool(soil_imp)) %>%
      as_tibble() %>%
      rownames_to_column("row") )

response_CIs <-   
  bind_rows(
    mutate(soil_terms, response = 'Temp. at surface'), 
    mutate(canopy_terms, response = 'Temp. above surface'),
    mutate(ros_terms, response = "Rate of spread") 
  ) %>%
  as_tibble() %>%
  rename(lwr = `2.5 %`, upr = `97.5 %`) %>%
  filter(term != '(Intercept)') %>%
  mutate(term = recode(term, tHa = 'Fuel load', 
                             WindSpeed = 'Wind speed', 
                             RH = 'Relative humidity', 
                             FuelMoisture = 'Fuel moisture', 
                             VPD = 'Vapor Pressure Deficit')) 
save(response_CIs, file = paste0(wd, 'r objects/response_CIs.Rdata'))
```

@@

```{r }
response_CIs %>%
  filter(response == "Rate of spread") %>%
  rename(t = statistic, 
         P = p.value) %>%
    select(term, t, P) %>%
  mutate(across(t:P, ~round(., 2))) %>%
  pander::pander("Summary statistics for Rate of spread.") 
```

@@

```{r }
response_CIs %>%
  filter(response == "Temp. above surface") %>%
  rename(t = statistic, 
         P = p.value) %>%
    select(term, t, P) %>%
  mutate(across(t:P, ~round(., 2))) %>%
  pander::pander("Summary statistics for flame temperature 15 cm above soil surface.") 
```

@@

```{r }
response_CIs %>%
  filter(response == "Temp. at surface") %>%
  rename(t = statistic, 
         P = p.value) %>%
    select(term, t, P) %>%
  mutate(across(t:P, ~round(., 2))) %>%
  pander::pander("Summary statistics for soil surface temperature.") 
```

@@

```{r}
# Testing for differences between locations 
pca_fc <-  envfit( fb_pca ~ location, imp_raw, 
                   choices = c(1:3), 
                   strata = imp_raw$year, 
                   199)$factors
pca_fc
```

>>>>

```{r}
 AnalysisData %>% 
          select(-LAI, -JD) %>%
  ggplot(aes(x=tHa)) + theme_bw(16) + 
              geom_histogram(aes(y=..density..),      
                 binwidth=0.1,
                 colour="black",
                 fill="lightgreen")

AnalysisData %>%
  select(SoilMaxC) %>%
  quantile(c(0.25, 0.5, .59, 0.6, 0.75), na.rm = T)
```

```{r imp, eval=TRUE}
# Calculate imputed datasets on scaled data
  imp_sc <- AnalysisData %>% 
          select(-LAI, -JD) %>%
          mutate(ros = ifelse(ros >= 12, NA, ros), 
                 tHa = ifelse(tHa >= 4, NA, tHa)) %>%
          mutate_at(vars(AirTemp:tHa), ~as.numeric(scale(., center=F))) %>%
                    mutate(across(location:array, as.factor)) %>%
                     mice(m=50, seed = 23109, print=F)

# Reduce mids object to tibble for multivariate analysis    
    imp_raw <- 
      complete(imp_sc, 'long') %>%
      as_tibble() %>%
      unite("TreeID", c(location, block, pasture,
                        year, plot, array), sep = ".") %>%
      select(-patch, -.id, -.imp, -FireCode) %>%
      pivot_longer(names_to = "response", 
                   values_to = "values", 
                   -TreeID) %>%
      group_by(TreeID, response) %>%
      summarize(value = median(values)) %>%
      ungroup() %>%
      pivot_wider(names_from = response, 
                  values_from = value) %>%
      separate(TreeID, c("location", "block", "pasture",
                         "year", "plot", "array")) %>% 
      mutate(across(location:array, as.factor))
```

@@

```{r data_summary_gg, fig.height=10, fig.width=6}
LongData <- 
  AnalysisData %>%
    select(-LAI, -JD, -MaxWindSpeed) %>%
    mutate(ros = ifelse(ros >= 10, NA, ros)) %>%
    pivot_longer(cols = AirTemp:tHa, 
                 names_to = 'var', 
                 values_to = 'value') %>%
    mutate(type = case_when(
                    var %in% c('MaxC', 
                               'SoilMaxC', 
                               'ros') ~ 'Fire behavior', 
                    var %in% c('tHa',
                               'FuelMoisture') ~ 'Fuel', 
                    TRUE ~ 'Weather' ), 
           var = recode(var, 
                        AirTemp = 'Air temperature (°C)', 
                        RH = 'Relative humidity (%)', 
                        dpC = 'Dew point (°C)', 
                        FuelMoisture = 'Fuel moisture (%)', 
                        tHa = 'Fuel load (t/ha)',
                        MaxC = 'Flame temp (°C)', 
                        WindSpeed = 'Wind speed (m/s)', 
                        ros = 'Rate of spread (m/s)', 
                        SoilMaxC = 'Soil surface temp (°C)'), 
           location = recode(location, 
                             H = "Hettinger", 
                             CG = "Central Grasslands"))

@@

```{r glmer_mods, eval=TRUE}
# Mixed-effect regression models 
#
# Rate of spread
#   
  # Fit model 
# ros_VPD <- with(imp_sc, suppressMessages(
#               lme4::glmer(ros ~ VPD + RH + tHa +
#                                 FuelMoisture + WindSpeed +
#                                 (1|location/block/year/plot), 
#                           family=Gamma(link = "log"), 
#                           control=lme4::glmerControl(optimizer="bobyqa", 
#                                                      optCtrl=list(maxfun=100000)) )) )

ros_RH <- with(imp_sc, suppressMessages(
              lme4::glmer(ros ~ RH + tHa +
                                FuelMoisture + WindSpeed +
                                (1|location/block/year/plot), 
                          family=Gamma(link = "log"), 
                          control=lme4::glmerControl(optimizer="bobyqa", 
                                                     optCtrl=list(maxfun=100000)) )) )
D1(ros_VPD, ros_RH) # Different

  # Get terms
    ros_terms <- 
      full_join(
      summary(pool(ros_RH)) %>% 
        as_tibble() %>%
        rownames_to_column("row"),

      confint.mipo(pool(ros_RH)) %>%
        as_tibble() %>%
        rownames_to_column("row") )

#
# Maximum canopy temperature  
#
# Fit model 
# canopy_VPD <- with(imp_sc, suppressMessages(
#               lme4::glmer(MaxC ~ VPD + RH + tHa +
#                               FuelMoisture + WindSpeed +
#                             (1|location/block/year/plot), 
#                           family=Gamma(link = "log"), 
#                           control=lme4::glmerControl(optimizer="bobyqa", 
#                                                      optCtrl=list(maxfun=100000)) )) )

canopy_RH <- with(imp_sc, suppressMessages(
              lme4::glmer(MaxC ~ RH + tHa +
                              FuelMoisture + WindSpeed +
                            (1|location/block/year/plot), 
                          family=Gamma(link = "log"), 
                          control=lme4::glmerControl(optimizer="bobyqa", 
                                                     optCtrl=list(maxfun=100000)) )) )

D1(canopy_VPD, canopy_RH) # not different

  canopy_RH_pooled <- pool(canopy_RH)$pooled  %>%
                      as_tibble()

  canopy_terms <- 
    full_join(
      summary(pool(canopy_RH)) %>% 
        as_tibble() %>%
        rownames_to_column("row"),

      confint.mipo(pool(canopy_RH)) %>%
        as_tibble() %>%
        rownames_to_column("row") )

#
# Maximum soil surface temperature  
#
# Fit model 
  # soil_VPD <- with(imp_sc, suppressMessages(
  #                 lme4::glmer(log(SoilMaxC+1) ~ VPD + RH + tHa +
  #                             FuelMoisture + WindSpeed +
  #                             (1|location/block/year/plot), 
  #                   family=Gamma(link = "log"), 
  #                   control=lme4::glmerControl(optimizer="bobyqa", 
  #                                              optCtrl=list(maxfun=100000)) )) )

  soil_RH <- with(imp_sc, suppressMessages(
                  lme4::glmer(log(SoilMaxC+1) ~ RH + tHa +
                              FuelMoisture + WindSpeed +
                              (1|location/block/year/plot), 
                    family=Gamma(link = "log"), 
                    control=lme4::glmerControl(optimizer="bobyqa", 
                                               optCtrl=list(maxfun=100000)) )) )

  D1(soil_VPD, soil_RH) # Not different

soil_RH_pooled <- pool(soil_RH)$pooled  %>%
  as_tibble()

soil_terms <- 
  full_join(
    summary(pool(soil_RH)) %>% 
      as_tibble() %>%
      rownames_to_column("row"),

    confint.mipo(pool(soil_RH)) %>%
      as_tibble() %>%
      rownames_to_column("row") )

response_CIs <-   
  bind_rows(
    mutate(soil_terms, response = 'Temp. at surface'), 
    mutate(canopy_terms, response = 'Temp. above surface'),
    mutate(ros_terms, response = "Rate of spread") 
  ) %>%
  as_tibble() %>%
  rename(lwr = `2.5 %`, upr = `97.5 %`) %>%
  filter(term != '(Intercept)') %>%
  mutate(term = recode(term, tHa = 'Fuel load', 
                             WindSpeed = 'Wind speed', 
                             RH = 'Relative humidity', 
                             FuelMoisture = 'Fuel moisture')) 
save(response_CIs, file = paste0(wd, 'r objects/response_CIs.Rdata'))
```

@@

```{r }
response_CIs %>%
  filter(response == "Rate of spread") %>%
  rename(t = statistic, 
         P = p.value) %>%
    select(term, df, t, P) %>%
  mutate(across(t:P, ~round(., 2))) %>%
  pander::pander("Summary statistics for Rate of spread.") 
```

@@

```{r }
response_CIs %>%
  filter(response == "Temp. above surface") %>%
  rename(t = statistic, 
         P = p.value) %>%
    select(term, df, t, P) %>%
  mutate(across(t:P, ~round(., 2))) %>%
  pander::pander("Summary statistics for flame temperature 15 cm above soil surface.") 
```

@@

```{r }
response_CIs %>%
  filter(response == "Temp. at surface") %>%
  rename(t = statistic, 
         P = p.value) %>%
    select(term, df, t, P) %>%
  mutate(across(t:P, ~round(., 2))) %>%
  pander::pander("Summary statistics for soil surface temperature.") 
```

@@

```{r}
# Testing for differences between locations 
pca_fc <-  envfit( fb_pca ~ location, imp_raw, 
                   choices = c(1:2), 
                   strata = imp_raw$year, 
                   199)$factors
pca_fc
```
